\section{Introduction}
\label{sec:introduction}

\begin{itemize}
%	relative food prices affect dietary quality
	\item \textbf{Use case 1: Keyword Query}\\
	 A data scientist wants to retrieve datasets with information related to Biomass Power Companies. Initially,  The user decides to start the search with a keyword-query $Q_{0,0} = $  (\{"biomass", "power", "companies"\}, $k = 10$). The search engine returns thirty datasets but none seem relevant to the user.
	 To retrieve more results the user decides to run the same query and increase $k$, $Q_{0,1} = $  (\{"biomass", "power", "companies"\}, $k = 20$). After the second attempt the search engine returns Table \ref{tab:q1-result1} (at position \#31) which contains data about biomass power plants per company. The user decides to keep Table \ref{tab:q1-result1} and continue to search for other relevant tables.\\
	
	\item \textbf{Use case 2: Join Query}
	Table \ref{tab:q1-result1} is relevant to $Q_{0,1}$ as it contains a list of biomass power plants, their location and capacity in Mega-Watt. However the user wants to include other information related to the prime mover of each plant, its status (operational or not), its start date etc.
	to explore other tables that may complement  Table \ref{tab:q1-result1} with more information, the data scientist selects a subset of plants based in California (from Table \ref{tab:q1-result1}),  and  performs a join query on the "Plant" column. \\*
	To avoid running the join query multiple times, the user chooses a high $k$ value at the expense of query time.
	$Q_{1,0} =$ ($\sigma_{Location = "\%CA\%"}$(Table \ref{tab:q1-result1}), Join column : "Plant", $k = 100$). The search engine returned $381$ results.\\* After skimming through the list of result, the user finds Table \ref{tab:q1-result2} at position \#315. Table \ref{tab:q1-result2} can be joined with Table \ref{tab:q1-result1} on the "Plant name" column. \\
	
\end{itemize}
Because the user has no prior knowledge of the total dataset size nor the optimal $k$ value to retrieve relevant results in the least time possible, the user chooses $k$ values randomly until he/she finds a relevant table.\\*
In use case 2 the user is unaware that the same result could be retrieved at position \#5 with $k = 10$.  \\* Due to a large number of results, It is also possible that the user does not notice the desired result and decides to further increase $k$. For example, suppose that in use case 2 the user did not notice the result at position \#315 and decided to submit $Q_{1,1} =$ ($\sigma_{Location = "\%CA\%"}$(Table \ref{tab:q1-result1}), Join column : "Plant", $k = 200$). The search engine will return 755 results, and Table \ref{tab:q1-result2} would be at position \#235.

\begin{table*}[p!]
	\setlength\extrarowheight{2pt} % for a bit of visual "breathing space"
	\begin{tabular}{ |l|p{2cm}|p{3cm}|p{2cm}|l|  }
		\hline
		\textbf{Company}&	\textbf{Plant}&	\textbf{Location}&	\textbf{Feedstock}&	\textbf{Capacity (MW)}\\
		\hline
		Wheelabrator Technologies Inc.& 	Wheelabrator Shasta Energy Co. Inc.& 	Anderson - CA& 	Logging and Mill Residue/Ag Residue& 	50\\
		\hline
		Greenleaf Power LLC& 	Desert View& 	Mecca - CA& 	Ag Residue/Urban Wood Waste& 	47\\
		\hline
		Greenleaf Power LLC& 	Honey Lake& 	Wendel - CA&	Mill and Logging Residue/Forest Thinning/Urban Woodwaste& 	30\\
		\hline
		Covanta& 	Covanta Delano& 	Delano - CA& 	Orchard and Vineyard Prunings/Nut Shells/Stone Fruit Pits& 	58\\
		\hline
		... & ... & ... & ... & ...\\
		\hline
		
	\end{tabular}
	\vspace{.2cm}
	\caption{U.S. Biomass Power Plants\label{tab:q1-result1}}
\end{table*}
	

\begin{table*}[p!]
	\setlength\extrarowheight{2pt} % for a bit of visual "breathing space"
	\begin{tabular}{ |l|p{1cm}|p{2cm}|p{1cm}|l|p{2cm}|p{1cm}|p{2cm}|p{2cm}|p{1cm}|p{1cm}|  }
		\hline
		Category& 	Plant ID& 	Plant Name& 	Unit& 	Status& 	Start Date& 	Retire Date& 	Prime mover ID& Prime Mover Description& Capacity& net MWh\\
		\hline
		 E& E0027& 	Desert View Power (Mecca Plant)& 	GEN1& 	OP& 	1991/11/1& 	-	&ST& 	Steam Turbine& 	54.15& 	351291\\
		 \hline
		 E & 	E0041& 	HL Power Company (Honey Lake)& 	GEN 1& 	OP& 	1989/7/26& 	-	&ST& 	Steam Turbine& 	35.5& 	200712\\
		 \hline
		 E& E0029& 	Covanta Delano, Inc& 	Delano 1-2& 	OP& 	1990/6/12& 	- &ST& 	Steam Turbine& 	58& 	322731\\
		 \hline
		 E& 	E0086& 	Wheelabrator Shasta& 	Units 1-3& 	OP& 	1987/1/1& 	-	&ST& 	Steam Turbine& 	54.9& 	405628\\
		 \hline
		 ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
		 
		\hline
		
		
	\end{tabular}
	\vspace{.2cm}
	\caption{Annual Generation - Plant Unit\label{tab:q1-result2}}
\end{table*}

